\textbf{Case Studies II - Community Talks}

### 2013-04-01 ricardogarfe/final_report/000-community-talks.tex
Refactor AZLinux file name.

\include{001-apache-community-talk}
\include{002-webkit-community-talk}
\include{003-plan9-community-talk}
\include{004-mozilla-community-talk}
\include{005-gnu-project-community-talk}
\include{006-open-document-community-talk}
\include{007-libre-desktop-laws-community-talk}
\include{008-wikipedia-community-talk}
\include{009-liferay-community-talk}
\include{010-azlinux-migration-commuinty-talk}
\include{011-gnome-community-talk}
\include{012-thunderbird-community-talk}
\include{013-canonical-community-talk}
\include{014-osor-community-talk}
\include{015-kde-community-talk}

\begin{thebibliography}{9}

    \bibitem{thunderbird-talk}
    Thunderbird Community Talk,\\
    Ludovic Hirliman,\\  
    Part 1,\\
    \url{http://blip.tv/mswl/case-studie-ii_quality-assurance-in-thunderbird-and-mozilla-5906218},\\
    Part 2 Questions and Answers,\\
    \url{http://blip.tv/mswl/case-studie-ii_quality-assurance-in-thunderbird-and-mozilla-5906218}

\end{thebibliography}

>>>>

\include{001-apache-community-talk}
\include{002-webkit-community-talk}
\include{003-plan9-community-talk}
\include{004-mozilla-community-talk}
\include{005-gnu-project-community-talk}
\include{006-open-document-community-talk}
\include{007-libre-desktop-laws-community-talk}
\include{008-wikipedia-community-talk}
\include{009-liferay-community-talk}
\include{010-azlinux-migration-community-talk}
\include{011-gnome-community-talk}
\include{012-thunderbird-community-talk}
\include{013-canonical-community-talk}
\include{014-osor-community-talk}
\include{015-kde-community-talk}
